

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,a4paper,roman]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

%\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.85]{geometry} % Reduce document margins
\setlength{\hintscolumnwidth}{2.2cm} % Uncomment to change the width of the dates column
\setlength{\makecvtitlenamewidth}{08cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name






%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Priyank} % Your first name
\familyname{Trivedi} % Your last name

% All information in this block is optional, comment out any lines you don't need
%\title{Machine leing engineer}
\address{\href{http://www.vit.ac.in}{VIT University}}{School of Computing Sciences and Engineering, India}
\mobile{(+1) 902-999-1868}

\email{priyankt68@gmail.com}
%\email{priyank.trivedi2010@vit.ac.in}
\homepage{www.priyanktrivedi.org}{www.priyanktrivedi.org} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
\extrainfo{\href{https://www.linkedin.com/in/priyankt68}{LinkedIn Profile}}
%\href{https://www.github.com/priyankt68}{Github: github.com/priyankt68}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{Currently: Visiting Undergraduate Researcher at Dalhousie University, Canada}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	Objective
%----------------------------------------------------------------------------------------

%\section{Objective}



%\section{Research Interests}


%\cvitem{}{{}{  \begin{itemize}
%  \item Machine Learning
%		\begin{itemize}
%			\item Support Vector Machine and Decision Trees and its performance on large scale daataset.
%			\item Predictive Analytics using Bayesian Learning.
%		\end{itemize}
%  \item High Performance Computing
%		\begin{itemize}
%			\item Heterogenous Computing involving GPU and CPU, especially Intel's MIC and Nvidia's CUDA framework.
%		\end{itemize}\end{itemize}}{}{}}

\section{Selected Coursework}

\cvitem{Computer Science}{{}{Programming Fundamentals $\cdot$ Theory of Computation $\cdot$ Computer Architecture and Organisation Computer Networks  $\cdot$ Operating Systems $\cdot$ Artificial Intelligence   $\cdot$ Object Oriented Systems \& Programming $\cdot$ Database Systems $\cdot$ Multicore Programming  $\cdot$ Computer Graphics }{}{}}

\cvitem{Mathematics}{{}{Multivariable Calculus $\cdot$ Linear Algebra $\cdot$ Discrete Mathematics $\cdot$ Probability and Applied Statistics   }{}{}}
\cvitem{MOOCs}{{}{"Machine Learning", Coursera, 88.7 \%}{, Andrew  Ng}{, Stanford University.}}






%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cvitem{2010--2014}{{Bachelors of Technology, Computer Science and Engineering, }{\href{http://www.vit.ac.in}{ VIT University,}}{ Chennai Campus, India}{ }{ \begin{itemize}
  \item CGPA- 8.69/10
  \item Undergraduate Thesis Advisor- \href{https://web.cs.dal.ca/~arc/index.html}{Dr. Andrew Rau-Chaplin}, Dalhousie University, Halifax, Canada.
   %\item Department Rank: 12/120.
   \item Graduating in June 2014.\end{itemize} } }

\cventry{References}{Dr. Andrew Rau-Chaplin}{Professor}{Faculty of Computer Science}{Dalhousie University, Canada}{Undergraduate Thesis Advisor. arc@cs.dal.ca} 
\cventry{}{Dr. L. Jeganathan}{Professor}{Dean, School of Computing Sciences and Engineering}{VIT University, India.  jeganathan.l@vit.ac.in}{} 
\cventry{}{Dr. K. Muthunagai}{Professor}{School of Advanced Sciences}{VIT University, India}{muthunagai@vit.ac.in} 

%\cventry{2007--2008}{High School}{Seth Anandram Jaipuria School}{Kanpur}{\textit{94.6 per cent}}{}

%%%%%%%%%%%%%%%%%%%%5
%Research Experience
%%%%%%%%%%%%%%%%5%%%%

\section{Research Experience}

\cventry{Jan - Jul 2014}{Visiting Undergraduate Researcher}{\href{http://web.cs.dal.ca/~arc/RiskAnalyticsLab/}{Risk Analytics Lab}}{Dalhousie University}{Halifax, Canada}{ \begin{itemize}	
	\item Exploiting parallelism in Barnes-Hut-SNE and Vantage Point Tree.
	\item Performance evaluation of Tree construction on Intel MIC and Nvidia's GPUs.
	\end{itemize}}

%\cventry{Mar - Nov 2013}{Sub-Editor}{Aol CoolAge}{}{}{ \begin{itemize}	
%	\item Member of \href{http://www.coolage.in}{CoolAge} Editorial Team
%	\end{itemize}}

\cventry{May - Jul 2012}{Summer Research Intern}{NeST Technologies}{Technology Development Centre}{Trivandrum, India}{\begin{itemize}	
	\item Developed a framework for reconstruction of 3D objects and their modelling using image processing algorithms to iteratively stitch multiple three dimensional scenes together to form a 3D model.
	\item Framework is highly useful for modelling internal spacing of buildings and object prototypes.
	\end{itemize}} 


%----------------------------------------------------------------------------------------
%	PUBLICATION  SECTION
%----------------------------------------------------------------------------------------

\section{Publications}

\cvitem{MMSC'13}{{\textbf{Priyank Trivedi}, Tejaswi Agarwal, K. Muthunagai,}{\href{http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=6637380}{\textbf{"MC-RANSAC: A Pre-processing Model
for RANSAC using Monte Carlo method implemented on a GPU",}} }{2\textsuperscript{nd} International Workshop on Mathematical Modelling and Scientific Computing, in conjunction with 2\textsuperscript{nd} IEEE International Conference on Advances in Computing, Communications and Informatics 2013}{ }}

\cvitem{PRIP'13}{Saurabh Jha, {\textbf{Priyank Trivedi},}{\href{http://goo.gl/4CwJrJ}{\textbf{"An Automated Video Surveillance System Using Viewpoint Feature Histogram and CUDA-enabled GPUs",}} }{2\textsuperscript{nd} International Symposium on Pattern Recognition and Image Processing, in conjunction with 2\textsuperscript{nd} IEEE International Conference on Advances in Computing, Communications and Informatics 2013}{ }}


\cvitem{SRS'13}{{Zeon Trevor Fernando}{,\textbf{Priyank Trivedi},Abhinandan Patni,Priyal Trivedi,}{\textbf{ \href{http://rpsonline.com.sg/proceedings/9789810773939/html/081.xml}{"DOCAID: Predictive Healthcare Analytics using Naive Bayes Theorem"}}}{}{ Published in proceedings of 2\textsuperscript{nd} \href{http://www.icacci-conference.org/srs2013}{Student Research Symposium, 2\textsuperscript{nd} IEEE International Conference on Advances in Computing,Communications and Informatics, India 2013} }} 

\cvitem{SET VIT'13}{{Abhinandan Patni,\textbf{ Priyank Trivedi}, Zeon Trevor Fernando, Tejaswi Agarwal,}{\textbf{"An Improvement in the build process of kd-tree"}}{ 6\textsuperscript{th} International Conference on Science Engineering and Technology}}

%----------------------------------------------------------------------------------------
%	technical SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Technical Skills}

\cventry{Programming Languages}{C, C++, Python, CUDA C}{}{}{}{}
\cventry{Operating Systems}{Linux Mint, Ubuntu, Windows}{}{}{}{}
\cventry{Web Languages}{HTML, CSS, Javascript}{}{}{}{}
\cventry{Open Source Technologies}{\LaTeX, Octave, MySQL, MongoDB}{}{}{}{}
\cventry{Libraries}{OpenMP, Thrust, scikit-learn, NLTK, Point Cloud Library }{}{}{}{}

%----------------------------------------------------------------------------------------
%	Projects SECTION
%----------------------------------------------------------------------------------------

\section{Projects }

%\subsection{Active \hfill{\href{http://www.priyanktrivedi.org/projects/projects.html}{Details on website}}}



%-------1-------%



\cvitem{Jan'14}{\textbf{Exploiting parallelism in Barnes-Hut-SNE and Vantage Point Tree for Nearest Neighbour Search}  \phantom{  Random textsdfjdfsdfdfdsfsdf sd}{\textbf{Project Advisor:} Dr. Andrew Rau-Chaplin   \href{https://github.com/priyankt68/vptree} { Github}}}
\cvitem{}{This project is a part of my Undergraduate Thesis at Risk Analytics Lab.It aims to exploit parallelism in t-Stochasitic Neighbour Embedding algorithm used for dimensionality reduction.}

%-------2-------%
\cvitem{Feb'14}{\textbf{Multi-class Image Classification} \hfill{\href{https://github.com/priyankt68/tagme-iisc}{Github}} }{}

\cvitem{}{The project is one of the instances of supervised learning technique in which images are tagged to one of the classes based on the training data.Random Forests and Support Vector Machines with assortment of kernels are employed to train classifiers and evaluate their runtime performance and accuracy. }

%-------3-------%

\cvitem{Mar'14}{\textbf{Reddit Miner: Mining Trending Stories through keywords} \hfill{\href{ https://github.com/priyankt68/reddit_miner}{Github} }}{}

\cvitem{}{Reddit Miner is a focussed crawler developed from scratch with MongoDB and Pymongo to perform text mining on Reddit.com.Based on user input ketword, Reddit Minner would produce stories related to it top 100 trending stories on reddit's technology page.}

%-------4-------%


\cvitem{Nov'13}{\textbf{k-means Clustering for Image Compression} \hfill{\href{https://github.com/priyankt68/kmeans_image_compression}{Github} } }{}

\cvitem{}{Project employs unsupervised learning technique, k-means clustering, to reduce the size of the image by reducing the number of colour representation.It clusters different colours representing the image and results in just 16 colour representation of the image. These 16 colours are chosen using Principal Component Analysis.}


%\subsection{Completed}

\cvitem{May'13}{\textbf{MC-RANSAC: A Pre-processing Model for RANSAC using Monte Carlo method implemented on a GPU}  }{}

\cvitem{}{Developed a novel RANdom SAmpling Consensus algorithm with pre-processing of the assumed sample set of hypothetical inliers by Monte Carlo method on a Graphic Processor.The results are a significant improvement in the performance of Plane Segmentation algorithm of Point Cloud Library on Nvidia's CUDA framework.}


\cvitem{Apr'13}{\textbf{An Automated Video Surveillance System Using Viewpoint Feature Histogram and CUDA-enabled GPUs}  }{}

\cvitem{}{Developed an Automated Video Surveillance System for content monitoring and activity change using Viewpoint Feature Histogram, an image descriptor for object recognition and pose estimation, of Point Cloud Library. The system operates on a heterogenous platform utilising the data intensive task of surveillance on CUDA-enabled devices alongwith Microsoft Kinect.}

\cvitem{Mar'13}{\textbf{DOCAID: Predictive Healthcare Analytics using Naive Bayes Theorem}  }{}

\cvitem{}{DOCAID is a platform for clinicians to perform healthcare analytics and helps them determine the probability of a patient suffering from a particular disease. In our system, we implement Naive Bayes classification, which takes in the patient's symptoms and complaints and successfully classifies it into an appropriate disease.}


\cvitem{Mar'12}{\textbf{EditText++: Text Editor } \hfill{\href{http://priyankt68.github.io/Editext/}{Github}} }{}

\cvitem{}{A simple text editor developed as Windows Form Application for HTML-CSS editing , basic formatting and password encryption techniques. One of the key features developed was file encryption unique to every file.}



%----------------------------------------------------------------------------------------
%	Scholastic Achievements
%----------------------------------------------------------------------------------------
%\section{Scholastic Achievements}

%\cventry{Fall 2012-13}{Department Rank 3 out of strength of 120 students}{Amity University}{}{}{}
%\cventry{April 2010}{Awarded NCC A-level Certificate}{Government of India}{}{}{}
%\cventry{July 2008}{Ranked 4 in a batch of 230 students}{ICSE}{with 96.4 \textit{percent}}{}{}

%---------------------------------------------
%References
%---------------------------------------------

%\section{References}







%----------------------------------------------------------------------------------------
%	Position of Responsibility
%----------------------------------------------------------------------------------------

%\section{Positions of Responsibility}



%\cventry{Jan 2012-13}{Joint Secretary}{Debate Society}{Amity University}{}{} 
%\cventry{Apr 2012-13}{Organizing Head}{"Robotron", an Annual Technical Festival organised at Amity University, Lucknow}{}{}{}
%\cventry{Mar 2013-present}{Vice President for Marketing}{\href{http://www.aiesec.in/‎}{AIESEC} Lucknow}{a largest student managed organisation in the world}{}{}
%\cventry{Mar 2013-present}{Member}{Citizens for Accountable Governance, India}{a non-profit organisation which aims to strengthen accountable governance in India}{}{}





%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage

%\recipient{HR Departmnet}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

%\makelettertitle % Print letter title

%\lipsum[1-3] % Dummy text

%\makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document}
